Api Gateway: Kong vs. AWS

### 2024-08-30 article.tex
chore: ennumerate doc files

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

@@

% Document content
\input{docs/introduction.tex}
\input{docs/api_gateway.tex}
\input{docs/kong.tex}
\input{docs/tbd.tex}
\input{docs/benchmark.tex}
\input{docs/conclucion.tex}

>>>>

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Cloud computing e infraestructura para Big Data]{Make sure to enter the correct
  conference title from your rights confirmation emai}{Agosto 31-08,
  2024}{Santa Cruz, Bolivia}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Bravo Peña}
\author{Darlyn}
\affiliation{
  \institution{UAGRM}
  \city{Santa Cruz}
  \country{Bolivia}
}
\email{bpdarlyn@gmail.com}

\author{Torrejón Mendez}
\author{Joel Gabriel}
\affiliation{
  \institution{UAGRM}
  \city{Santa Cruz}
  \country{Bolivia}
}
\email{joel.torrejon.mendez@gmail.com}

\author{Valle Tamayo}
\author{Brandon Jason}
\affiliation{
  \institution{UAGRM}
  \city{Santa Cruz}
  \country{Bolivia}}
\email{bjvtamayo78@gmail.com}
%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Bravo - Torrejón - Valle}

@@

% Document content
\input{docs/1_introduction.tex}
\input{docs/2_api_gateway.tex}
\input{docs/3_kong.tex}
\input{docs/4_tbd.tex}
\input{docs/5_benchmark.tex}
\input{docs/6_conclucion.tex}
